### 2014-03-12 src/methodology.Rnw
udpate

Next, we modified this criteria slightly, and instead of choosing a mutant
with probability of decimal part, applied \texit{round(sample)} to round
it to the nearest whole number. We used this as the number of samples to
be chosen from the population. Our aim was to remove elements that was
too simple. That is, if the number of mutants dropped below a threshold
determined by the mutant reduction ratio, that program element did not
contribute any thing to the final result.

>>>>

Next, we modified this criteria slightly, and instead of choosing a mutant
with probability of decimal part, applied \textit{round(sample)} to round
it to the nearest whole number. We used this as the number of samples to
be chosen from the population. Our aim was to remove elements that was
too simple. That is, if the number of mutants dropped below a threshold
determined by the mutant reduction ratio, that program element did not
contribute any thing to the final result.
